The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-03-07 paper/ms.tex
Added discussion of fudge factor for completeness estimate

@@

We show the total survey completeness in Figure \ref{fig:completeness}. The completeness falls very rapidly towards low mass ratios, although we are still $\sim 70\%$ complete at $q = 0.1$. The slow fall-off towards large mass ratios is caused by the same effect as in Figure \ref{fig:marginalized}: large mass ratio companions tend to be rapid rotators that are more difficult to detect.

TODO: Discuss fudge factor if Adam agrees...

@@

    HIP 2912 &      B5V &    00:36:52.85 &   +33:43:09.64 &   4.360 &      5.45 &  $16000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.7^{+0.61}_{-0.54}$ &      $26^{+32}_{-18}$ &       2 \\

@@

    HIP 3741 &      B9V &    00:48:01.06 &   -21:43:20.99 &   5.570 &      9.51 &   $10000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.8^{+0.47}_{-0.42}$ &    $282^{+82}_{-115}$ &       2 \\
    HIP 3881 &      B5V &    00:49:48.85 &   +41:04:44.08 &   4.530 &      5.28 &  $16000 \pm 1000$ &  $4.2 \pm 0.25$ &  $4.5^{+0.58}_{-0.52}$ &      $17^{+28}_{-11}$ &       2 \\
    HIP 4436 &      A5V &    00:56:45.21 &   +38:29:57.64 &   3.870 &     25.14 &    $8351 \pm 284$ &  $4.0 \pm 0.14$ &  $1.9^{+0.17}_{-0.14}$ &   $733^{+129}_{-158}$ &       1 \\

@@

    HIP 5348 &  B6V+B9V &    01:08:23.08 &   -55:14:44.73 &   3.967 &     10.92 &   $13776 \pm 468$ &  $4.2 \pm 0.14$ &  $3.6^{+0.23}_{-0.21}$ &      $67^{+38}_{-39}$ &       1 \\

@@

   HIP 14143 &      B7V &    03:02:22.52 &   +04:21:10.39 &   5.607 &      5.93 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.50}_{-0.45}$ &      $17^{+36}_{-11}$ &       2 \\

@@

   HIP 14576 &      B8V &    03:08:10.13 &   +40:57:20.33 &   2.120 &     36.27 &   $13070 \pm 444$ &  $4.0 \pm 0.14$ &  $3.6^{+0.29}_{-0.24}$ &     $139^{+16}_{-25}$ &       1 \\

@@

   HIP 16147 &      B5V &    03:28:03.07 &   +49:03:46.32 &   4.970 &      6.22 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.59}_{-0.58}$ &       $11^{+14}_{-5}$ &       2 \\

@@

   HIP 18724 &      B3V &    04:00:40.82 &   +12:29:25.22 &   3.410 &      6.74 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\

@@

   HIP 25048 &      B3V &    05:21:48.42 &   +41:48:16.46 &   5.200 &      6.16 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.5^{+0.62}_{-0.61}$ &       $11^{+13}_{-5}$ &       2 \\

@@

   HIP 25281 &      B1V &    05:24:28.62 &   -02:23:49.73 &   3.350 &      3.34 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\

@@

     HR 1880 &    B0.5V &    05:35:08.48 &   +09:56:06.10 &   6.322 &   \nodata &  \nodata          &  \nodata        &  \nodata                &         \nodata          &       \nodata \\

@@

   HIP 33575 &      B2V &    06:58:35.90 &   -25:24:50.97 &   5.577 &      3.78 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.69}_{-0.67}$ &         $8^{+6}_{-3}$ &       2 \\

@@

     HR 2948 &      B6V &    07:38:49.38 &   -26:48:06.49 &   4.500 &   \nodata &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.48}_{-0.44}$ &      $17^{+36}_{-11}$ &       2 \\

@@

   HIP 55266 &      A2V &    11:19:07.90 &   +38:11:08.03 &   4.800 &     17.00 &    $8720 \pm 296$ &  $4.5 \pm 0.14$ &  $1.9^{+0.10}_{-0.08}$ &   $346^{+208}_{-217}$ &       1 \\

@@

     HR 5476 &      A6V &    14:40:43.94 &   +16:25:03.90 &   5.820 &   \nodata &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\

@@

   HIP 78821 &      B2V &    16:05:26.57 &   -19:48:06.85 &   4.890 &      8.19 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\

@@

   HIP 85998 &      A2V &    17:34:36.69 &   +09:35:12.12 &   5.810 &      9.66 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.44}_{-0.37}$ &   $399^{+137}_{-200}$ &       2 \\

@@

   HIP 96840 &      B5V &    19:41:05.53 &   +13:48:56.45 &   5.988 &      0.49 &  $16000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.7^{+0.62}_{-0.56}$ &      $26^{+31}_{-18}$ &       2 \\

@@

   HIP 98194 &      B5V &    19:57:13.87 &   +40:22:04.17 &   5.453 &      2.94 &  $16000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.7^{+0.59}_{-0.54}$ &      $27^{+31}_{-19}$ &       2 \\

@@

  HIP 100881 &      B4V &    20:27:19.21 &   -18:12:42.20 &   5.250 &      5.98 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.48}_{-0.45}$ &      $17^{+34}_{-10}$ &       2 \\

@@

  HIP 101867 &      A0V &    20:38:31.34 &   +21:12:04.25 &   4.820 &     14.01 &   $10507 \pm 357$ &  $4.2 \pm 0.14$ &  $3.4^{+0.24}_{-0.30}$ &     $252^{+45}_{-33}$ &       1 \\

@@

  HIP 104019 &      A5V &    21:04:24.30 &   -19:51:17.97 &   4.840 &     20.20 &    $8319 \pm 283$ &  $4.2 \pm 0.14$ &  $1.8^{+0.09}_{-0.07}$ &   $452^{+245}_{-273}$ &       1 \\

@@

  HIP 111841 &      O9V &    22:39:15.68 &   +39:03:00.97 &   4.880 &      1.89 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\

@@

    HIP 2912 &  7238.96 &     IGRINS &      367 &   130 \\
    HIP 2912 &  6583.78 &       TS23 &      199 &  2460 \\

@@

    HIP 3741 &  7174.89 &     CHIRON &     3981 &   430 \\
    HIP 3741 &  7175.90 &     CHIRON &     3561 &   420 \\
    HIP 3881 &  6585.70 &       TS23 &      222 &  1690 \\
    HIP 3881 &  6964.60 &       TS23 &     1200 &   710 \\
    HIP 3881 &  6945.74 &     IGRINS &      224 &   200 \\
    HIP 4436 &  6585.76 &       TS23 &      129 &  1940 \\

@@

    HIP 5348 &  6325.56 &     CHIRON &      186 &   390 \\

@@

   HIP 14143 &  6518.94 &        HRS &      462 &   900 \\

@@

   HIP 14576 &  6583.83 &       TS23 &       40 &  1030 \\
   HIP 14576 &  6582.92 &       TS23 &       36 &  2050 \\

@@

   HIP 16147 &  6299.59 &       TS23 &      735 &  1300 \\

@@

   HIP 18724 &  6299.62 &       TS23 &      226 &  1220 \\

@@

   HIP 25048 &  6299.69 &       TS23 &      900 &   420 \\

@@

   HIP 25281 &  6299.71 &       TS23 &      583 &  1120 \\

@@

     HR 1880 &  6594.74 &     CHIRON &      472 &   540 \\

@@

   HIP 33575 &  6599.72 &     CHIRON &     1200 &   390 \\

@@

     HR 2948 &  6584.81 &     CHIRON &      576 &   370 \\

@@

   HIP 55266 &  6300.00 &       TS23 &      900 &   200 \\

@@

     HR 5476 &  6408.71 &        HRS &      305 &   660 \\

@@

   HIP 78821 &  7139.84 &     IGRINS &      210 &    50 \\

@@

   HIP 85998 &  7122.96 &     IGRINS &      480 &    50 \\
   HIP 85998 &  7230.64 &     IGRINS &      720 &   170 \\
   HIP 85998 &  6407.84 &        HRS &      324 &   490 \\
   HIP 85998 &  7079.89 &     CHIRON &     1600 &   220 \\

@@

   HIP 98194 &  6583.54 &       TS23 &      495 &  1750 \\

@@

  HIP 100881 &  6511.69 &     CHIRON &     1011 &   570 \\

@@

  HIP 101867 &  6489.78 &     CHIRON &      408 &   440 \\

@@

  HIP 104019 &  6474.90 &     CHIRON &      423 &   550 \\

@@

  HIP 111841 &  6583.68 &       TS23 &      267 &  1670 \\

@@

  HIP 14576 & Aa,Ab &     2 & no &  $6980 \pm 103$ &      10 &     0.0  &  $1.4^{+0.03}_{-0.03}$ &  $1.5^{+0.05}_{-0.03}$ \\

@@

  HIP 18724 & AB &     1 & no &  $6831 \pm 154$ &      20 &     0.0  &  $1.7^{+0.13}_{-0.23}$ &  $1.4^{+0.04}_{-0.04}$ \\

@@

  HIP 55266 & AB &     1 & no &  $8483 \pm 139$ &      30 &    -0.5 &  $1.8^{+0.06}_{-0.04}$ &  $2.0^{+0.06}_{-0.05}$ \\

@@

  HIP 85998 & Aa,Ab &     3 & yes &  $5460 \pm 91$ &      1 &    -0.5  &  $1.0^{+0.28}_{-0.03}$ &  $0.9^{+0.04}_{-0.01}$ \\

>>>>

We test to determine if the completeness is reasonable at large mass ratios by comparing to known binary systems. We detect 15 of the 25 stars in our sample with a hot ($T > 7000\ K$) companion. The completeness function for hot, roughly equal-mass companions suggest the probability of detection if $\sim 80\%$, which is incompatible with our low detection rate (p=0.01). The discrepancy may be due to an underestimate of the typical rotation rates for hot stars, used when marginalizing out the dependence on $v\sin{i}$. Additionally, rapidly rotating companions, especially when they have a similar temperature to the primary, are more difficult to detect if they have a small radial velocity offset from the primary star. While the injection and recovery experiments do sample velocity space to account for this, they may be over-sampling companions with very large velocity offsets and producing anomalously high detection rates. We account for the discrepancy by introducing a scaling factor: we multiply the estimated detection rate for all companions with $T > 7000\ K$ by $f=0.8$.

@@

We show the resulting total survey completeness in Figure \ref{fig:completeness}. The completeness falls very rapidly towards low mass ratios, although we are still $\sim 60\%$ complete at $q = 0.1$. The slow fall-off towards large mass ratios is caused by a combination of the scale factor described above and the inherent difficulty of detecting rapidly rotating companions (see Figure \ref{fig:marginalized}). The detection rate at large mass ratios is now $\sim 0.6-0.7$, which is consistent with our 15/25 empirical detection rate.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@
